Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-06 inc/model_results/lens_charge/lens_charge.tex
merge comments on lens_charge section

\section{Space-charge Effects in Magnetic Lenses} \label{sec:mag_lens_charge}

In the transverse spatial dimension, space-charge effects that increase $ \sigma_{ \smallT } $ can be compensated for by using magnetic electron lenses.\cite{oudheusden_electron_2007,lagrange_nanosecond_2008}
In an UEM, of course, the electron pulse will also need to be focused onto the specimen --- the focal spot size, post specimen image magnification, and CCD detector pixelation determining the spatial resolution in a TEM geometry.\cite{berger_dc_2009}
The extent to which space-charge effects limit the focal fidelity is expected to be dependent upon both $N$ and the pulse shape (i.e., the pulse's space-time eccentricity).

In the preceding sections it has already been established that oblate eccentricities are preferred for UEM in general.
When focusing the pulse it can be shown that oblate pulses will also have markedly better performance.

@@

\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for intially oblate ($ \xi ( 0 ) = 0.1 $) or prolate ($ \xi ( 0 ) = 10 $) pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm and a `short' focal length of 6.0mm.
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, this simulation again uses the idealistic initial conditions set; the pulses used are at 20kV velocity with $\Delta E = $ 0.5eV but are not simulated using an accelerator.
As such the simulation presented approximates a beam which has been perfectly collimated at the front-focal plane of the lens.

>>>>

\section{Space-charge Effects and Spatial Focusing} \label{sec:mag_lens_charge}

In the transverse spatial dimension, space-charge effects that increase $ \sigma_{ \smallT } $ can be compensated for by using magnetic electron lenses.\cite{oudheusden_electron_2007,lagrange_nanosecond_2008}
In an UEM, of course, the electron pulse will also need to be focused onto the specimen --- the focal spot size, post specimen image magnification, and CCD detector pixelation determining the spatial resolution in a TEM geometry.\cite{berger_dc_2009}
The extent to which space-charge effects limit the focal fidelity is expected to be dependent upon both $N$ and the pulse shape (i.e., the pulse's space-time eccentricity), while still subject to Liouville's Theorem (see Section \ref{sec:liouville}).

@@

In the preceding sections it has already been established that oblate eccentricities are preferred for UEM in general.
When focusing the pulse it can be shown that oblate pulses will also have markedly better performance.
\ref{fig:focus_lens_charge} shows the predicted dynamics of the spatial electron pulse waist (HW1/eM) for intially oblate ($ \xi ( 0 ) = 0.1 $) or prolate ($ \xi ( 0 ) = 10 $) pulses under perfect focusing for lenses of two focal lengths; a `long' focal length of 60mm and a `short' focal length of 6.0mm.
The pulse's initial volume is constant in all cases ($w_{\smallT}^2 w_{z} = (232 \mu\text{m})^3$).
For both lens strengths, the deleterious effects of space-charge are evident as the number of electrons/pulse $ N $ is increased.
To make an effective comparison, highlighting the effect of space-charge alone, this simulation again uses the idealistic initial conditions set; the pulses used are at velocity associated with a 30kV energy and have momentum variance associated with $\Delta E = $ 0.5eV, but are not simulated using an emitter and accelerator.
As such the simulation presented approximates a beam which has been nearly perfectly collimated at the focus of a long focal-length lens.
